HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-03-30 LaTeX/ms.tex
Comments + plotseds
95% of comments complete.  Plot SEDs to inspect flux densities from J.
Scudders.

\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
C.~Hayward\altaffilmark{3,4},
W.~Cowley\altaffilmark{5},
J.~Bock\altaffilmark{6,7},
J.~Calanog\altaffilmark{8},
A.~Cooray\altaffilmark{8},
F.~De Bernardis\altaffilmark{8},
R.~Hopwood\altaffilmark{9},
M.~Jarvis\altaffilmark{10},
C.~Lacey\altaffilmark{5},
A.~Loeb\altaffilmark{4},
S.~J.~Oliver\altaffilmark{11},
I.~P{\'e}rez-Fournon\altaffilmark{12,13},
I.~G.~Roseboom\altaffilmark{11,14},
A.~J.~Smith\altaffilmark{11},
L.~Wang\altaffilmark{11},
J.~Wardlow\altaffilmark{15}}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{6}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{7}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{8}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{9}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{10}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{11}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{12}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{13}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{14}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  We
    identify a total of 62 sources down to the $5\sigma$ limit in our ALMA
    sample ($\sigma \approx 0.2\,$mJy).  Optical or near-infrared imaging
    indicates that 36 of the ALMA sources experience a significant flux boost
    from gravitational lensing ($\mu > 1.1$), but only 6 are strongly lensed
    and show multiple images.  Combined with our previous work on brighter {\it
    Herschel} sources, the lens models presented here constrain the shape of
    the intrinsic luminosity function for DSFGs to have a break near 8$\,$mJy
    at 880$\,\mu$m with a very steep fall off at higher flux densities.  We
    introduce and make use of {\sc uvmcmcfit}, a general purpose and publicly
    available Markov chain Monte Carlo visibility plane analysis tool to
    analyze the source properties.  Nearly 70\% of the {\it Herschel} sources
    break down into multiple ALMA counterparts, consistent with previous
    research indicating that the multiplicity rate is high in bright sources
    discovered in single-dish sub-mm or FIR surveys.  The ALMA counterparts to
    our {\it Herschel} targets are located much closer to each other than ALMA
    counterparts to sources found in the LABOCA ECDFS Submillimeter Survey.
    Theoretical models underpredict the excess number of sources with small
    separations seen in our ALMA sample.  The high multiplicity rate and low
    projected separations between sources seen in our sample argue in favor of
    interactions and mergers plausibly driving both the prodigious emission
    from the brightest DSFGs as well as the sharp downturn above $S_{880} =
    8\,$mJy.

@@

Our collective understanding of DSFGs is currently taking a dramatic leap
forward thanks in large part to the {\it Herschel Space Observatory}
\citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has revolutized the size and
depth of blind surveys at FIR wavelengths.  In particular, the {\it Herschel}
Multi-tiered Extragalactic Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it
Herschel} Astrophysical Terahertz Large Area Survey
\citep[H-ATLAS;][]{2010PASP..122..499E} together have surveyed $\approx
650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m to the confusion
limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a level
approximately double the confusion limit.  A similar effort to survey large
areas of the sky has been undertaken at longer wavelengths by the South Pole
Telescope \citep[SPT;][]{Carlstrom:2011qy} and the Atacama Cosmology Telescope
\citep{Swetz:2011qy}.

Theoretical expectations based on the redshift distribution and luminosity
function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools for
discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
2007MNRAS.377.1557N}.  Submillimeter Array \citep[SMA;][]{Ho:2004lr} imaging at
870$\,\mu$m with sub-arcsecond resolution has confirmed this, with $\geq 85\%$
of the brightest sources found by {\it Herschel} ($S_{500} > 100\,$mJy) being
gravitationally lensed by an intevening galaxy or group of galaxies along the
line of sight \citep{Negrello:2010fk, Conley:2011lr, Riechers:2011uq,
Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
surveys have also been shown to have a high probability of being strongly lensed
\citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
significantly over-predict the median magnification factor experienced by a {\it
Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
indicate a deficiency in our understanding of the bright end of the intrinsic
DSFG luminosity function.

@@

\caption{ ALMA 870$\,\mu$m images (color scale, units of mJy$\,$beam$^{-1}$) of HerMES
DSFGs (images have not been corrected for primary beam attenuation).  Contours
(black and white) trace 250$\,\mu$m emission from {\it Herschel}.  The FWHM
size of the ALMA synthesized beam is shown in the lower left corner of each
panel.  A solid white circle shows the FWHM size of the primary beam.  Dashed
squares identify the regions of each image that are shown in greater detail in
Fig.~\ref{fig:uvmodels}.  \label{fig:imaging}} \addtocounter{figure}{-1}

@@

In {\sc uvmcmcfit}, lens mass profiles are represented by $N_{\rm lens}$
singular isothermal ellipsoid (SIE) profiles, where $N_{\rm lens}$ is the
number of lensing galaxies found from the best available optical or near-IR
imaging \citep[a multitude of evidence supports the SIE as a reasonable choice;
for a recent review, see][]{Treu:2010fk}.  Each SIE is fully described by the
following five free parameters: the position of the lens on the sky relative to
the arbitrarily chosen ``image center'' based on the ALMA 870$\,\mu$m emission
and any lensing galaxies seen in the optical or near-IR ($\Delta \alpha_{\rm
lens}$ and $\Delta \delta_{\rm lens}$; these can be compared with the position
of the optical or near-IR counterpart relative to the ``image center'': $\Delta
\alpha_{\rm NIR}$ and $\Delta \delta_{\rm NIR}$), the mass of the lens
(parameterized in terms of the angular Einstein radius, $\theta_{\rm E}$), the
axial ratio of the lens ($q_{\rm lens} = b_{\rm lens} / a_{\rm lens}$), and the
position angle of the lens ($\phi_{\rm lens}$; degrees east of north).  Unless
otherwise stated, when optical or near-IR imaging suggests the presence of
additional lenses (see Figure~\ref{fig:uvmodels}), we estimate centroids for
each lens by eye and fix the positions of the additional lenses with respect to
the primary lens.  Each additional lens thus has three parameters:
$\theta_{\rm E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.  We assume secondary,
tertiary, etc., lenses are located at the same redshift as the primary lens.

@@

@@

{\bf HECDFS12:} This is a complex, well-constrained system.  Two sources are
detected by ALMA: one is strongly lensed and the other is weakly lensed.  In
addition, the lens is detected by ALMA (this is one of two sources in the
entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These facts
work together to provide very tight constraints on the system.  Since the lens
is detected by ALMA, its position relative to the lensed images is unambiguous.
Also, because there is a strongly lensed source with multiple images, the
Einstein radius of the lens is unambiguous.  A byproduct of these two facts is
that the magnification factor of the weakly lensed source is known to very high
precision as well.  It experiences a magnification factor of $\mu_{870} =
1.520\pm0.002$ despite being located $\approx4\arcsec$ north of the lens (which
has an Einstein radius of $1.353\pm0.005$; it is the tight constraint on the
Einstein radius that permits such a tight constraint on $\mu_{870}$ for the
weakly lensed source).  We use these numbers to inform our estimates of the
Einstein radius for weakly lensed sources without the excellent contraints
provided by this system.  Finally, this source is detected (and unresolved) in
the NRAO VLA Sky Survey \citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8
\pm 0.8\,$mJy.  Assuming all of this radio emission originates from the lens,
this implies a spectral slope of $\alpha = -0.24$ and is consistent with
non-thermal emission from the lens.

@@

{\bf HADFS10:} Three sources are detected by ALMA.  We 
assume that all three are unlensed.  There is a group of three sources
detected in our Gemini-S optical imaging located $\approx 7\arcsec$ east of the
ALMA sources.  This distance is so large that plausible mass ranges for the
Gemini-S sources would imply at most a factor of 1.1$-$1.2 boost in the apparent
flux densities of the ALMA sources.

@@

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  There is greater overlap in $S_{870}$ between our sample and
ALESS than there is in $S_{500}$ (recall Figure~\ref{fig:sample}).  This is
evidence that the DSFGs in our sample have higher $S_{500}/S_{870}$ ratios than
the DSFGs in ALESS.  This difference is likely due to differences in dust
temperature and/or redshift distributions of the two samples and probably arises
from selection effects.

@@

In Table~\ref{tab:models}, we provide information for two models tested in this
paper: the \citet{Karim:2013lr} broken power-law that provides a good fit to
ALESS number counts; and a broken power-law with a brighter break point
($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
from \citet{Miettinen:2015lr}.  The data and corresponding luminosity functions
are shown in the left panel of Figure~\ref{fig:lensstats}.

>>>>

\author{R.~S.~Bussmann\altaffilmark{1},
D.~Riechers\altaffilmark{1},
A.~Fialkov\altaffilmark{2},
C.~Hayward\altaffilmark{3,4},
W.~Cowley\altaffilmark{5},
J.~Bock\altaffilmark{6,7},
J.~Calanog\altaffilmark{8},
A.~Cooray\altaffilmark{8},
F.~De Bernardis\altaffilmark{8},
R.~Hopwood\altaffilmark{9},
M.~Jarvis\altaffilmark{10},
C.~Lacey\altaffilmark{5},
A.~Loeb\altaffilmark{4},
S.~J.~Oliver\altaffilmark{11},
I.~P{\'e}rez-Fournon\altaffilmark{12,13},
I.~G.~Roseboom\altaffilmark{11,14},
A.~J.~Smith\altaffilmark{11},
L.~Wang\altaffilmark{11},
J.~Wardlow\altaffilmark{15}}
\altaffiltext{$\dagger$}{Herschel is an ESA space observatory with science
instruments provided by European-led Principal Investigator consortia and with
important participation from NASA.}
\altaffiltext{1}{Department of Astronomy, Space Science Building, Cornell University, Ithaca, NY, 14853-6801}
\altaffiltext{2}{Departement de Physique, Ecole Normale Sup erieure, CNRS, 24 rue Lhomond, Paris, 75005 France}
\altaffiltext{3}{TAPIR 350-17, California Institute of Technology, 1200 E. California Boulevard, Pasadena, CA 91125}
\altaffiltext{4}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{5}{Institute for Computational Cosmology, Department of Physics, University of Durham, South Road, Durham, DH1 3LE, UK}
\altaffiltext{6}{California Institute of Technology, 1200 E. California Blvd., Pasadena, CA 91125}
\altaffiltext{7}{Jet Propulsion Laboratory, 4800 Oak Grove Drive, Pasadena, CA 91109}
\altaffiltext{8}{Dept. of Physics \& Astronomy, University of California, Irvine, CA 92697}
\altaffiltext{9}{Astrophysics Group, Imperial College London, Blackett Laboratory, Prince Consort Road, London SW7 2AZ, UK}
\altaffiltext{10}{Centre for Astrophysics Research, University of Hertfordshire, College Lane, Hatfield, Hertfordshire AL10 9AB, UK}
\altaffiltext{11}{Astronomy Centre, Dept. of Physics \& Astronomy, University of Sussex, Brighton BN1 9QH, UK}
\altaffiltext{12}{Instituto de Astrof{\'\i}sica de Canarias (IAC), E-38200 La Laguna, Tenerife, Spain}
\altaffiltext{13}{Departamento de Astrof{\'\i}sica, Universidad de La Laguna (ULL), E-38205 La Laguna, Tenerife, Spain}
\altaffiltext{14}{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK}
\altaffiltext{15}{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 Copenhagen, Denmark}

@@

    The {\it Herschel} Multi-tiered Extragalactic Survey (HerMES) has
    identified large numbers of dusty star-forming galaxies (DSFGs) over a wide
    range in redshift.  A detailed understanding of these DSFGs is hampered by
    the poor spatial resolution of {\it Herschel}.  We present 870$\,\mu$m
    0$\farcs$45 imaging obtained in Cycle~0 with the Atacama Large
    Millimeter/submillimeter Array (ALMA) of a sample of 29 HerMES DSFGs.  The
    ALMA imaging reveals that these DSFGs comprise a total of 62 sources (down
    to the $5\sigma$ limit in our ALMA sample; $\sigma \approx 0.2\,$mJy).
    Optical or near-infrared imaging indicates that 36 of the ALMA sources
    experience a significant flux boost from gravitational lensing ($\mu >
    1.1$), but only 6 are strongly lensed and show multiple images.  Combined
    with our previous work on brighter {\it Herschel} sources, the lens models
    presented here constrain the shape of the intrinsic luminosity function for
    DSFGs to have a break near 8$\,$mJy at 880$\,\mu$m with a very steep fall
    off at higher flux densities.  We introduce and make use of {\sc
    uvmcmcfit}, a general purpose and publicly available Markov chain Monte
    Carlo visibility plane analysis tool to analyze the source properties.
    Nearly 70\% of the {\it Herschel} sources break down into multiple ALMA
    counterparts, consistent with previous research indicating that the
    multiplicity rate is high in bright sources discovered in single-dish
    sub-mm or FIR surveys.  The ALMA counterparts to our {\it Herschel} targets
    are located significantly closer to each other than ALMA counterparts to
    sources found in the LABOCA ECDFS Submillimeter Survey.  Theoretical models
    underpredict the excess number of sources with small separations seen in
    our ALMA sample.  The high multiplicity rate and low projected separations
    between sources seen in our sample argue in favor of interactions and
    mergers plausibly driving both the prodigious emission from the brightest
    DSFGs as well as the sharp downturn above $S_{880} = 8\,$mJy.

@@

Our collective understanding of DSFGs is currently taking a dramatic leap
forward thanks in large part to the {\it Herschel Space Observatory}
\citep[{\it Herschel};][]{Pilbratt:2010fk}.  This has revolutized the size and
depth of blind surveys at FIR wavelengths.  In particular, the {\it Herschel}
Multi-tiered Extragalactic Survey \citep[HerMES;][]{Oliver:2012lr} and the {\it
Herschel} Astrophysical Terahertz Large Area Survey
\citep[H-ATLAS;][]{2010PASP..122..499E} together have surveyed $\approx
650\,$deg$^2$ at 250$\,\mu$m, 350$\,\mu$m, and 500$\,\mu$m to the confusion
limit of {\it Herschel} \citep[$\sigma \approx 6-7\,$mJy in each
band][]{Nguyen:2010fk}, plus an additional $\approx 350\,$deg$^2$ to a
shallower level (approximately double the confusion limit).  A similar effort
to survey large areas of the sky has been undertaken at longer wavelengths by
the South Pole Telescope \citep[SPT;][]{Carlstrom:2011qy} and the Atacama
Cosmology Telescope \citep{Swetz:2011qy}.

Theoretical expectations based on the redshift distribution and luminosity
function of DSFGs suggested that HerMES and H-ATLAS would be efficient tools
for discovering strongly lensed DSFGs \citep[e.g.,][]{1996MNRAS.283.1340B,
2007MNRAS.377.1557N}.  Submillimeter Array \citep[SMA;][]{Ho:2004lr} imaging at
870$\,\mu$m with sub-arcsecond resolution has confirmed this, with $\geq 85\%$
of the brightest sources found by {\it Herschel} ($S_{500} > 100\,$mJy) being
gravitationally lensed by an intervening galaxy or group of galaxies along the
line of sight \citep{Negrello:2010fk, Conley:2011lr, Riechers:2011uq,
Bussmann:2012lr, Wardlow:2013lr, Bussmann:2013lr}.  Sources discovered in SPT
surveys have also been shown to have a high probability of being strongly
lensed \citep{Vieira:2013fk, Hezaveh:2013fk}.  However, statistical models
significantly over-predict the median magnification factor experienced by a
{\it Herschel} DSFG of a given $S_{500}$ \citep{Bussmann:2013lr}.  This could
indicate herald new insights in our understanding of the bright end of the
intrinsic DSFG luminosity function or in the nature of the deflectors.

@@

\caption{ ALMA 870$\,\mu$m images (color scale, units of mJy$\,$beam$^{-1}$) of
HerMES DSFGs (images have not been corrected for primary beam attenuation).
Contours (black and white) trace 250$\,\mu$m emission from {\it Herschel}
(starting at 4$\sigma$ and increasing by factors of 2, where $\sigma=7\,$mJy).
The FWHM size of the ALMA synthesized beam is shown in the lower left corner of
each panel.  A solid white circle shows the FWHM size of the primary beam.
Dashed squares identify the regions of each image that are shown in greater
detail in Fig.~\ref{fig:uvmodels}.  \label{fig:imaging}}
\addtocounter{figure}{-1}

@@

In {\sc uvmcmcfit}, lens mass profiles are represented by $N_{\rm lens}$
singular isothermal ellipsoid (SIE) profiles, where $N_{\rm lens}$ is the
number of lensing galaxies found from the best available optical or near-IR
imaging \citep[a multitude of evidence supports the SIE as a reasonable choice;
for a recent review, see][]{Treu:2010fk}.  Each SIE is fully described by the
following five free parameters: the position of the lens on the sky relative to
the arbitrarily chosen ``image center'' based on the ALMA 870$\,\mu$m emission
and any lensing galaxies seen in the optical or near-IR ($\Delta \alpha_{\rm
lens}$ and $\Delta \delta_{\rm lens}$; these can be compared with the position
of the optical or near-IR counterpart relative to the ``image center'': $\Delta
\alpha_{\rm NIR}$ and $\Delta \delta_{\rm NIR}$), the mass of the lens
(parameterized in terms of the angular Einstein radius, $\theta_{\rm E}$), the
axial ratio of the lens ($q_{\rm lens} = b_{\rm lens} / a_{\rm lens}$), and the
position angle of the lens ($\phi_{\rm lens}$; degrees east of north).  Unless
otherwise stated, when optical or near-IR imaging suggests the presence of
additional lenses (see Figure~\ref{fig:uvmodels}), we estimate centroids for
each lens by eye and fix the positions of the additional lenses with respect to
the primary lens.  Each additional lens thus has three parameters: $\theta_{\rm
E}$, $q_{\rm lens}$, and $\phi_{\rm lens}$.

@@

We assume secondary, tertiary, etc., lenses are located at the same redshift as
the primary lens.  If this assumption were incorrect, to first order only the
conversion from an angular Einstein radius to a physical mass of the lensing
galaxy would be affected.  As the physical masses of the lensing galaxies are
not the focus of this work, this assumption is reasonable.

@@

{\bf HECDFS12:} This is a complex, well-constrained system.  Two background
sources are detected by ALMA: one is multiply imaged and the other is singly
imaged.  In addition, the lens is detected by ALMA (this is one of two sources
in the entire {\it Herschel}-ALMA sample that is unresolved by ALMA).  These
facts work together to provide very tight constraints on the system.  Since the
lens is detected by ALMA, its position relative to the lensed images is
unambiguous.  Also, because there is a strongly lensed source with multiple
images, the Einstein radius of the lens is unambiguous.  A byproduct of these
two facts is that the magnification factor of the weakly lensed source is known
to very high precision as well.  It experiences a magnification factor of
$\mu_{870} = 1.520\pm0.002$ (note that this error bar is valid under the
assumptions of our model, most notably the assumption that the singly imaged
source is located at the same redshift as the multiply imaged source; the true
uncertainty is likely a factor of a few larger).  despite being located
$\approx4\arcsec$ north of the lens (which has an Einstein radius of
$1.353\pm0.005$; it is the tight constraint on the Einstein radius that permits
such a tight constraint on $\mu_{870}$ for the weakly lensed source).  We use
these numbers to inform our estimates of the Einstein radius for weakly lensed
sources without the excellent contraints provided by this system.  Finally,
this source is detected (and unresolved) in the NRAO VLA Sky Survey
\citep{Condon:1998uq}, having $S_{\rm 1.4\,GHz} = 21.8 \pm 0.8\,$mJy.  Assuming
all of this radio emission originates from the lens, this implies a spectral
slope of $\alpha = -0.24$ and is consistent with non-thermal emission from the
lens.

@@

{\bf HADFS10:} Three sources are detected by ALMA.  We assume that all three
are unlensed.  There is a group of three sources detected in our Gemini-S
optical imaging located $\approx 7\arcsec$ east of the ALMA sources.  This
distance is so large that plausible mass ranges for the Gemini-S sources would
imply at most a factor of 1.1$-$1.2 boost in the apparent flux densities of the
ALMA sources.  We also tested a single-lens, single-source model in which the
source is triply-imaged in the manner that is observed.  The lens in this case
has an Einstein radius of $\approx 1\farcs2$, requiring a very high mass to
light ratio or a very high lens redshift to be consistent with the
non-detection in the Gemini-S data.  Deep near-IR imaging is needed to confirm
that this target is unlensed.

@@

For comparison, we also show the cumulative distribution of $S_{870}$ for the
ALESS sample.  ALESS is the only existing sample of DSFGs with interferometric
follow-up of a sensitivity and angular resolution that is comparable to our
ALMA data, so it is the best sample with which to compare our results.  There
is greater overlap in $S_{870}$ between our sample and ALESS than there is in
$S_{500}$ (recall Figure~\ref{fig:sample}).  This is evidence that the DSFGs in
our sample have higher $S_{500}/S_{870}$ ratios than the DSFGs in ALESS.  This
difference is likely due to differences in dust temperature and/or redshift
distributions of the two samples and probably arises from selection effects.

@@

In Table~\ref{tab:models}, we provide information for two models tested in this
paper: the \citet{Karim:2013lr} broken power-law that provides a good fit to
ALESS number counts; and a broken power-law with a brighter break point
($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
from \citet{Miettinen:2015lr}.  The interferometric observations in
\citet{Miettinen:2015lr} show that all of the sources in their survey are
either unlensed or lensed by magnification factors $<2$.  Therefore, the ALESS
and COSMOS luminosity functions bracket the plausible range of intrinsic
luminosity functions for DSFGs.  The data and corresponding luminosity
functions are shown in the left panel of Figure~\ref{fig:lensstats}.
